Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-04-11 talk/icooolps2011/paper.tex
add another note
fix one of maciej's comment, ignore two

XXX [fijal] yet another advantage is that JIT is by design supporting the whole
    language

@@

Tracing through the execution of an interpreter has many advantages. It makes
the tracer, its optimizers and backends reusable for a variety of languages. The
language semantics do not need to be encoded into the JIT. Instead the tracer
just picks them up from the interpreter.

@@

XXX [fijal] maybe it's worth noting that those guards are removed out of
    the loop by loop-invariant-code motion, unless our is so special
    we want to write a special paper about it

>>>>

@@

Tracing through the execution of an interpreter has many advantages. It makes
the tracer, its optimizers and backends reusable for a variety of languages. The
language semantics do not need to be encoded into the JIT. Instead the tracer
just picks them up from the interpreter. This also means that the JIT by
construction supports the full language.

@@
